### 2024-10-08 texts/paper_closing.tex
new title, abstract, word cutting, subheadings

% Created 2024-10-07 ma 14:02
% Intended LaTeX compiler: pdflatex
\documentclass[12pt]{article}

@@

\setlength{\parindent}{1.2cm}
\author{Johannes }
\date{\today}
\title{}
\hypersetup{
 pdfauthor={Johannes },
 pdftitle={},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 29.4 (Org mode 9.7.9)}, 
 pdflang={English}}
\begin{document}

\section*{Stayin' Alive: The unexpected longevity of founder-centered private art museums}

\subsection*{Introduction}

@@

While private collectors have existed for centuries, and have already founded a number of notable museums in the gilded age \parencite{Higonnet_2003_sight,Duncan_1995_civilizing}, in the recent decades they have substantially expanded their activities into the museum sphere by founding their own museums as individuals, rather than loaning or donating their collection or opening museums as a group.
This phenomenon of private collectors taking the initiative in setting up a museum of their own has become increasingly widespread, with around 80\% of currently open private museums having opened since 2000 \parencite{Velthuis_etal_2023_boom}.
To be considered as a private museum for this study, a collector needs to have amassed a substantial art collection, which he or she exhibits in a building in a way that is accessible to the public while receiving limited public and corporate funding.
The central role of the founder delimits a private museum from other organizational forms such as public museums supported by local or state governments, corporate museums run by companies or other non-profit museums operated by associations or foundations with more dispersed ownership and control.\footnote{Which is not to say that for an institution to be considered a private museum, it has to be legal personal ownership of the founder. Instead, the distinguishing criterion is the central role of the collector, which can be the case under a wide range of organizational forms; generally, this has to be assessed on a case-by-case basis.}

@@

Given that operating at "the margin of financial sustainability" is the "ordinary condition" for non-profit organizations (NPO) in the cultural sector, \parencite[p.2]{Licci_BaraldiBonini_2024_sustainability}, it is not surprising that costs have been listed as a primary reason for private museum closure:
\textcite{Adam_2021_rise} argues that "most of the cases of defunct private museums come back to the issue of cost" (p.79); a sentiment shared by \textcite{Walker_2019_collector} who notes that "private institutions struggle to contain escalating costs that are associated with running a museum" (p.234).
In other studies, "insufficient funding, high maintenance costs and lack of strong government support" \parencite[p.7]{Zennaro_2017_shanghai}, a "shortage of fundings and interruptions in cash" \parencite[p.45]{Song_2008_private}, bankruptcies \parencite{Velthuis_Gera_2024_fragility,Liu_2019_identities,DeNigris_2018_museums}, costly legal battles \parencite{Velthuis_Gera_2024_fragility}, stock devaluations \parencite{Walker_2019_collector} or failing auction sales \parencite{Bechtler_Imhof_2018_future} have been found as central reasons that forced private museums to close.
In a systematic review of closing reasons given in newspapers, magazines, social media accounts and personal exchanges, \textcite{Velthuis_Gera_2024_fragility} find financial issues as the most commonly mentioned reasons for private museum closing.
\subsubsection*{diversification}

@@

While limited research exists that investigates reputation effects for (art) museums, its effects have been investigated for non-profits more widely.
Here reputation is often referred to as an organization's resource or asset \parencite{Kong_Farrell_2010_image,Walker_McCarthy_2010_survival,Schloderer_Sarstedt_Ringle_2014_reputation}. 
Studies primarily focus on the effect of reputation on some tangible benefits such as donations and contributions \parencite{Sarstedt_2010_reputation,Mews_Boenigk_2012_blood,Heller_2008_alliances,Meijer_2009_reputation}, or its direct effect on survival \parencite{Lu_Shon_Zhang_2019_dissolution,Singh_1991_change,Hager_2001_vulnerability,Bielefeld_1994_survival,HernandezOrtiz_2022_discontinuity}, with most studies finding support for a positive effect of reputation.
Next to the reputation of the general public, studies have also found reputation effects among more narrowly defined groups, in particular peers \parencite{Padanyi_Gainer_2003_peerreputation} and networks of similar organizations on regional and national scale \parencite{Walker_McCarthy_2010_survival}.
In particular, this reputation among more narrowly defined groups makes it likely that the reputation of the \emph{founder} matters (beyond the reputation of the \emph{organization}, the focus on most prior research) given the highly personal character of the private museum initiative and the central role of the founder in negotiations with decision makers from other organizations or the public sector.

In the case of the founder losing their reputation, the consequences then might extend beyond personal demotivation.
Such a decline could also curtail potential opportunities for cooperation with other institutions and limit the museum's reach to larger audiences, thus posing a risk to the museum's continued operation and survival in the long term.
\bigbreak
\noindent
\textbf{Hypothesis 1b}: Private museums are more likely to close after a decline of their founder's status.

@@

\paragraph*{Founder death}

A measure of founder death is constructed as a time-varying covariate with values of 1 from the year of the founder's death onwards and 0 otherwise.
\paragraph*{Founder reputaton}

@@

% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Fri Sep 27 17:51:18 2024
\begin{table}[ht]
\centering
\begin{tabular}{lrll}
  \hline 
 \multicolumn{1}{l}{Self-identification} & \multicolumn{1}{l}{N} & \multicolumn{1}{l}{Self-ID (recoded)} & \multicolumn{1}{l}{examples}\\ 
 \hline
 Museum & 190 & Museum & Museum Kampa, Museum Barberini \\ 
  Foundation & 104 & Foundation & Marciano Art Foundation, Hill Art Foundation \\ 
  Collection &  69 & Collection & The Farjam Collection, Sammlung Boros \\ 
  None &  64 & Other & The Bunker, The Broad \\ 
  Center &  17 & Other & Dairy Art Centre, Art Center Nabi \\ 
  Gallery &  14 & Other & Saatchi Gallery, Galerie C15 \\ 
  Art space &  13 & Other & El Espacio 23, Qiao Space \\ 
  House / villa &  11 & Other & Villa La Fleur, Casa Daros Rio \\ 
  Institute &  10 & Other & Instituto Inhotim, Woods Art Institute \\ 
  Kunsthalle &   8 & Other & Kunsthalle Würth, G2 Kunsthalle \\ 
  Park / garden &   3 & Other & Schlosspark Eyebesfeld, Il Giardino dei Lauri \\ 
   \hline
\end{tabular}
\caption{Selfidentification} 
\label{tbl:t_selfid}
\end{table}

@@

To ensure that inclusion of the word "museum" corresponds to the naming convention of the museum population, the names of the "Museums of the World" (MOW) database \parencite{deGruyter_2021_MOW}, a database containing over 55,000 museums, are analyzed.
In this database, 71\% of museum names contain the term "museum" (or its equivalent in other languages), which indicates a substantial convention by founders to include the term museum in the name of their institution.\footnote{While it would also be possible to construct inclusion in the MOW as an indicator of legitimacy, as it represents recognition of the organization as a museum by experts, preliminary investigations of the database indicated that it has been updated only sparsely in recent years; thereby inclusion in it (or the lack therefore) does not constitute an accurate measurement of an institutions' recognition as a museum.}
At the same time, for an association between name and survival to be attributed to the name, the name and other organizational characteristics cannot be linked too closely.
This seems to be the case for museums, as organizations are not subject to strong regulations to be considered a museum: 
The term "museum" is not a protected term in the US \parencite[p.205]{Moore_2022_best} or European countries such as Germany \parencite[p.4]{Museumsbund_ICOMDE_2006_standards}, Denmark, Austria, Croatia or Finland \parencite{EGMUS_2024_reports}\footnote{While I was not able to find concrete information on the naming regulations of museums for every country, I did not find any country where such naming regulation is present.}.
Neither is membership in national or international museum associations necessary for an institution to be recognized as a museum: 
The International Council of Museums (ICOM) has around 3,000 institutional members \parencite{ICOM_2020_report19}, a relatively small fraction of the over 104,000 museums estimated to exist globally \parencite{UNESCO_2021_covid}, and while national associations fare somewhat better, with e.g. the American Association of Museums representing over 4,000 of the country's 35,000 museums \parencite{LOC_2019_AAM}, and the German Museumsbund representing over 1,300 \parencite{Museumsbund_2024_mitgliedmuseen} of Germany's 7,120 museums \parencite{IMF_2024_museumsstatistik}, the ability of these associations to impose standards is still limited.
In such a largely unregulated field, names do not clearly reflect institutional characteristics, which leaves evaluation of a museum to less institutionalized practical classification systems \parencite{van_Venrooij_2018_fuzziness}.
\paragraph*{Competition}

@@

% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Fri Oct  4 15:36:13 2024
\begin{table}[ht]
\centering
\begin{tabular}{llrrrrrr}
  \hline
 & & \multicolumn{2}{c}{Museum} & \multicolumn{4}{c}{Museum-year} \\ 
\cmidrule(r){3-4}\cmidrule(r){5-8} \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{Count} & \multicolumn{1}{l}{Mean} & \multicolumn{1}{l}{Mean} & \multicolumn{1}{l}{SD} & \multicolumn{1}{l}{Min.} & \multicolumn{1}{l}{Max.}\\ 
 \hline
  \multicolumn{8}{l}{\textbf{Founder}} \\ 
 & Gender - Male & 294 & 0.584 & 0.604 & 0.49 & 0 & 1 \\ 
   & Gender - Female & 79 & 0.157 & 0.166 & 0.37 & 0 & 1 \\ 
   & Gender - Couple & 130 & 0.258 & 0.231 & 0.42 & 0 & 1 \\ 
   & Founder died &  &  & 0.097 & 0.30 & 0 & 1 \\ 
   \multicolumn{8}{l}{\textbf{Museum}} \\ 
 & Self-Identification - Museum & 190 & 0.378 & 0.408 & 0.49 & 0 & 1 \\ 
   & Self-Identification - Foundation & 104 & 0.207 & 0.189 & 0.39 & 0 & 1 \\ 
   & Self-Identification - Collection & 69 & 0.137 & 0.130 & 0.34 & 0 & 1 \\ 
   & Self-Identification - Other & 140 & 0.278 & 0.274 & 0.45 & 0 & 1 \\ 
   & Founder name in Museum name & 240 & 0.477 & 0.477 & 0.50 & 0 & 1 \\ 
   & AN Ranking - Not Included &  &  & 0.802 & 0.40 & 0 & 1 \\ 
   & AN Ranking - Included &  &  & 0.144 & 0.35 & 0 & 1 \\ 
   & AN Ranking - Dropped &  &  & 0.053 & 0.23 & 0 & 1 \\ 
   \multicolumn{8}{l}{\textbf{Environment}} \\ 
 & PM density (country) &  &  & 0.450 & 1.26 & 0.00077 & 27.26 \\ 
   & Pop. (millions) within 10km &  &  & 1.337 & 1.68 & 0.000087 & 10.81 \\ 
   & Nbr PM within 10km &  &  & 1.778 & 3.14 & 0 & 16 \\ 
   & Great Recession (2008/09) &  &  & 0.076 & 0.27 & 0 & 1 \\ 
   & Covid Pandemic (2020/21) &  &  & 0.145 & 0.35 & 0 & 1 \\ 
   & Region - Africa & 8 & 0.016 & 0.012 & 0.11 & 0 & 1 \\ 
   & Region - Asia & 142 & 0.282 & 0.292 & 0.45 & 0 & 1 \\ 
   & Region - Europe & 248 & 0.493 & 0.497 & 0.50 & 0 & 1 \\ 
   & Region - Latin America & 23 & 0.046 & 0.042 & 0.20 & 0 & 1 \\ 
   & Region - North America & 72 & 0.143 & 0.138 & 0.34 & 0 & 1 \\ 
   & Region - Oceania & 10 & 0.020 & 0.019 & 0.13 & 0 & 1 \\ 
   \hline
\end{tabular}
\caption{Summary Statistics} 
\label{tbl:t_sumstats}
\end{table}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=16cm]{../figures/p_hazard.pdf}
\caption{\label{fig:p_hazard}Private Museum hazard function}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[width=14cm]{../figures/p_surv.pdf}
\caption{\label{fig:p_surv}Private Museum Survival probability}
\end{figure}

@@

Calculating such survival statistics allows (to a degree) to assess whether private museums differ in their longevity from comparable institutions.
So far only a few studies have investigated museum closing rates, and these have focused on the United States, likely primarily due to data availability reasons: 
Larger non-profits in the US have to file the IRS form 990 (or its variants) to maintain their tax-deductible status, and form 990 data is publicly available \parencite{Lecy_2023_core}.
This data has been used in many studies of non-profit populations and constitutes an effective comparison group for private museums as both share the same organizational form (non-profit) and unprofitable cultural sector environment.
So far three studies have used this data to investigate museum closure by calculating hazard rates not as a function of age but of calendar year:
\begin{itemize}
\item \textcite{Bowen_etal_1994_charitable} investigate the closing of 501(c)(3) museums in the 1981-1991 time period and, based on 271 (9.8\%) closures of a population of 2755, calculate average annual exit rates as 1.1\% (p.103).
\item \textcite{Gordon_etal_2013_insolvency} observe 35 closures based on 5,167 museum-years between 2000 and 2003 (p.368), resulting in an average annual closing rate of 0.68\% (p.377)\footnote{The difference to \cite{Bowen_etal_1994_charitable} is likely due to exclusion of organizations with revenues below 150,000 USD.}.
\item \textcite{Hager_2001_vulnerability} has conducted the only study specifically on art museums (NTEE code A51); he observes 42 closures over a period of four years (1994-1997) from a starting population of 448 (p.383), corresponding to an average yearly closing rate of 2.4\%, or around 1.9\% under the more realistic assumption of effectively using a five-year time period.
\end{itemize}

@@

% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Fri Sep 27 17:51:41 2024
\begin{table}[ht]
\centering
\begin{tabular}{p{0mm}lD{)}{)}{8)3}}
  \hline 
 \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{r\_pop4}\\ 
 \hline
  \multicolumn{3}{l}{\textbf{Founder}} \\ 
 & Gender - Female & -.04 \; (0.34) \\ 
   & Gender - Couple & -.14 \; (0.32) \\ 
   & Founder died & .28 \; (0.43) \\ 
   \multicolumn{3}{l}{\textbf{Museum}} \\ 
 & Self-Identification - Foundation & .20 \; (0.41) \\ 
   & Self-Identification - Collection & -.45 \; (0.54) \\ 
   & Self-Identification - Other & 1.09 \; (0.30)^{***} \\ 
   & AN Ranking - Included & .19 \; (0.34) \\ 
   & AN Ranking - Dropped & .46 \; (0.50) \\ 
   & Founder name in Museum name & .05 \; (0.28) \\ 
   \multicolumn{3}{l}{\textbf{Environment}} \\ 
 & PM density (country) & .65 \; (0.34) \\ 
   & PM density$^{2}$ (country) & -.03 \; (0.02) \\ 
   & Pop. (millions) within 10km & .27 \; (0.09)^{**} \\ 
   & Nbr PM within 10km & .26 \; (0.08)^{***} \\ 
   & Nbr PM (10km) * Pop (10km) & -.09 \; (0.03)^{**} \\ 
   & Great Recession (2008/09) & -1.59 \; (1.01) \\ 
   & Covid Pandemic (2020/21) & .42 \; (0.29) \\ 
   \hline
 & Museums & 503 \\ 
   & Museum-years & 6096 \\ 
   & Closures & 68 \\ 
   & log. Likelihood & -339.68 \\ 
   & AIC & 711.35 \\ 
   & BIC & 746.87 \\ 
   \hline 
 \multicolumn{3}{l}{\footnotesize{standard errors in parantheses.\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}} \\ 
\end{tabular}
\caption{Cox Proportional Hazards Regression Results} 
\label{tbl:t_reg_coxph}
\end{table}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=18cm]{../figures/p_surv_death.pdf}
\caption{\label{fig:p_surv_death}Comparison of Survival Estimates by Founder Death (95\% CI)}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=18cm]{../figures/p_condmef.pdf}
\caption{\label{fig:p_condmef}Conditional effects of Regional PM Density and Population}
\end{figure}

Country-level measures of the private museum population show a marginally significant association with mortality (b=0.648, p=0.058).
\begin{figure}[htbp]
\centering
\includegraphics[width=18cm]{../figures/p_pred_heatmap.pdf}
\caption{\label{fig:p_pred_heatmap}Predicted Avg. Hazard Rate on Regional PM Density and Population (at available values)}
\end{figure}

@@

Similarly, characterizations of private museums as generally fragile \cite{Adam_2020_close,Bechtler_Imhof_2018_future} are not supported here either.
While the descriptive comparison to other studies allows only preliminary conclusions, it still shows the importance of considering closings not in isolation, but in comparison to both non-closures and closures of comparable institutions.
In particular, the context of the growing private museum population deserves consideration, as large populations can generate dozens of closures without requiring high closing rates, especially when closures are considered over a span of several years or decades.

>>>>

% Created 2024-10-08 di 10:05
% Intended LaTeX compiler: pdflatex
\documentclass[12pt]{article}

@@

\setlength{\parindent}{1.2cm}
\author{Johannes Aengenheyster}
\date{\today}
\title{}
\hypersetup{
 pdfauthor={Johannes Aengenheyster},
 pdftitle={},
 pdfkeywords={},
 pdfsubject={},
 pdfcreator={Emacs 29.4 (Org mode 9.7.9)}, 
 pdflang={English}}
\begin{document}

\section*{The show must go on: Can private art museums survive?}

\subsection*{Abstract}

Hundreds of art collectors have decided to open their private art museums in the last decades.
As their numbers have grown, so have questions whether this new organizational form can endure in the long term.
Using a newly constructed database of 503 museums and 68 closures (6096 museum years), I use Cox Proportional Hazard models to investigate which factors increase the chance of private museum closure.
While most research has been skeptical of the long-term prospects, in particular as reliance on an individual founder has been seen as a risk factor, no significant association is found between the museum's likelihood to close and the death of the founder or their loss of status.
Instead, a museum's survival chances are found to depend primarily on its name (reflecting lack of recognition, or their founders' temporarily bounded plans) and location (reflecting complex competitive dynamics).
\subsection*{Introduction}

@@

While private collectors have existed for centuries, and have already founded a number of notable museums in the gilded age \parencite{Higonnet_2003_sight,Duncan_1995_civilizing}, in the recent decades they have substantially expanded their activities into the museum sphere by founding their own museums as individuals, rather than loaning or donating their collection or opening museums as a group.
This phenomenon of private collectors taking the initiative in setting up a museum of their own has become increasingly widespread, with around 80\% of currently open private museums having opened since 2000 \parencite{Velthuis_etal_2023_boom}.
To be considered as a private museum for this study, a collector needs to have amassed a substantial art collection, which he or she exhibits in a building in a way that is accessible to the public while receiving limited public and corporate funding.
The central role of the founder delimits a private museum from other organizational forms such as public museums supported by local or state governments, corporate museums run by companies or other non-profit museums operated by associations or foundations with more dispersed ownership and control.\footnote{Which is not to say that for an institution to be considered a private museum, it has to be legal personal ownership of the founder. Instead, the distinguishing criterion is the central role of the collector, which can be the case under a wide range of organizational forms and has to be assessed on a case-by-case basis.}
\subsubsection*{Financial conditions in the cultural sector}

@@

Given that operating at "the margin of financial sustainability" is the "ordinary condition" for non-profit organizations (NPO) in the cultural sector, \parencite[p.2]{Licci_BaraldiBonini_2024_sustainability}, it is not surprising that costs have been listed as a primary reason for private museum closure:
\textcite{Adam_2021_rise} argues that "most of the cases of defunct private museums come back to the issue of cost" (p.79); a sentiment shared by \textcite{Walker_2019_collector} who notes that "private institutions struggle to contain escalating costs that are associated with running a museum" (p.234).
In other studies, "insufficient funding, high maintenance costs and lack of strong government support" \parencite[p.7]{Zennaro_2017_shanghai}, a "shortage of fundings and interruptions in cash" \parencite[p.45]{Song_2008_private}, bankruptcies \parencite{Velthuis_Gera_2024_fragility,DeNigris_2018_museums}, costly legal battles \parencite{Velthuis_Gera_2024_fragility}, stock devaluations \parencite{Walker_2019_collector} or failing auction sales \parencite{Bechtler_Imhof_2018_future} have been found as central reasons that forced private museums to close.
In a systematic review of closing reasons given in newspapers, magazines, social media accounts and personal exchanges, \textcite{Velthuis_Gera_2024_fragility} find financial issues as the most commonly mentioned reasons for private museum closing.
\subsubsection*{The risks of relying on single founders}

@@

While limited research exists that investigates reputation effects for (art) museums, its effects have been investigated for non-profits more widely.
Here reputation is often referred to as an organization's resource or asset \parencite{Walker_McCarthy_2010_survival,Schloderer_Sarstedt_Ringle_2014_reputation}. 
Studies primarily focus on the effect of reputation on some tangible benefits such as donations and contributions \parencite{Sarstedt_2010_reputation,Mews_Boenigk_2012_blood,Heller_2008_alliances,Meijer_2009_reputation}, or its direct effect on survival \parencite{Lu_Shon_Zhang_2019_dissolution,Singh_1991_change,Hager_2001_vulnerability,Bielefeld_1994_survival,HernandezOrtiz_2022_discontinuity}, with most studies finding support for a positive effect of reputation.
Next to the reputation of the general public, studies have also found reputation effects among more narrowly defined groups, in particular peers \parencite{Padanyi_Gainer_2003_peerreputation} and networks of similar organizations on regional and national scale \parencite{Walker_McCarthy_2010_survival}.
In particular, this reputation among more narrowly defined groups makes it likely that the reputation of the \emph{founder} matters (beyond the reputation of the \emph{organization}, the focus on most prior research) given the highly personal character of the private museum initiative and the central role of the founder in negotiations with decision makers from other organizations or the public sector.

In the case of the founder losing their reputation, the consequences then might extend beyond personal demotivation.
Such a decline could also curtail potential opportunities for cooperation with other institutions and limit the museum's reach to larger audiences, thus posing a risk to the museum's continued operation and survival in the long term.
\bigbreak
\noindent
\textbf{Hypothesis 1b}: Private museums are more likely to close after a decline of their founder's status.
\subsubsection*{Environmental risks}

@@

\paragraph*{Founder Death}

A measure of founder death is constructed as a time-varying covariate with values of 1 from the year of the founder's death onwards and 0 otherwise.
\paragraph*{Founder Reputation}

@@

% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Fri Sep 27 17:51:18 2024
\begin{table}[ht]
\centering
\begin{tabular}{lrll}
  \hline 
 \multicolumn{1}{l}{Self-identification} & \multicolumn{1}{l}{N} & \multicolumn{1}{l}{Self-ID (recoded)} & \multicolumn{1}{l}{examples}\\ 
 \hline
 Museum & 190 & $Museum$ & Museum Kampa, Museum Barberini \\ 
  Foundation & 104 & $Foundation$ & Marciano Art Foundation, Hill Art Foundation \\ 
  Collection &  69 & $Collection$ & The Farjam Collection, Sammlung Boros \\ 
  None &  64 & $Other$ & The Bunker, The Broad \\ 
  Center &  17 & $Other$ & Dairy Art Centre, Art Center Nabi \\ 
  Gallery &  14 & $Other$ & Saatchi Gallery, Galerie C15 \\ 
  Art space &  13 & $Other$ & El Espacio 23, Qiao Space \\ 
  House / villa &  11 & $Other$ & Villa La Fleur, Casa Daros Rio \\ 
  Institute &  10 & $Other$ & Instituto Inhotim, Woods Art Institute \\ 
  Kunsthalle &   8 & $Other$ & Kunsthalle Würth, G2 Kunsthalle \\ 
  Park / garden &   3 & $Other$ & Schlosspark Eyebesfeld, Il Giardino dei Lauri \\ 
   \hline
\end{tabular}
\caption{Selfidentification} 
\label{tbl:t_selfid}
\end{table}

@@

To ensure that inclusion of the word "museum" corresponds to the naming convention of the museum population, the names of the "Museums of the World" (MOW) database \parencite{deGruyter_2021_MOW}, a database containing over 55,000 museums, are analyzed.
In this database, 71\% of museum names contain the term "museum" (or its equivalent in other languages), which indicates a substantial convention by founders to include the term museum in the name of their institution.\footnote{While it is also possible to measure legitimacy via inclusion in the MOW database, as it represents recognition of the organization as a museum by experts, preliminary investigations indicated that the MOW database has been updated too sparsely in recent years for inclusion in it (or the lack therefore) to constitute an accurate measurement of an institutions' legitimacy.}
At the same time, for an association between name and survival to be attributed to the name, the name and other organizational characteristics cannot be linked too closely.
This seems to be the case for museums, as organizations are not subject to strong regulations to be considered a museum: 
The term "museum" is not a protected term in the US \parencite[p.205]{Moore_2022_best} or European countries such as Germany \parencite[p.4]{Museumsbund_ICOMDE_2006_standards}, Denmark, Austria, Croatia or Finland \parencite{EGMUS_2024_reports}\footnote{While I was not able to find concrete information on the naming regulations of museums for every country, I did not find any country where such naming regulation is present.}.
Neither is membership in national or international museum associations necessary for an institution to be recognized as a museum: 
The International Council of Museums (ICOM) has around 3,000 institutional members \parencite{ICOM_2020_report19}, a relatively small fraction of the over 104,000 museums estimated to exist globally \parencite{UNESCO_2021_covid}, and while national associations fare somewhat better, with e.g. the American Association of Museums representing over 4,000 of the country's 35,000 museums \parencite{LOC_2019_AAM}, and the German Museumsbund representing over 1,300 \parencite{Museumsbund_2024_mitgliedmuseen} of Germany's 7,120 museums \parencite{IMF_2024_museumsstatistik}, the ability of these associations to impose standards is still limited.
In such a largely unregulated field, names do not clearly reflect institutional characteristics, which leaves evaluation of a museum to less institutionalized practical classification systems \parencite{van_Venrooij_2018_fuzziness}.
\paragraph*{Competition}

@@

% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Fri Oct  4 15:36:13 2024
\begin{table}[ht]
\centering
\begin{tabular}{llrrrrrr}
  \hline
 & & \multicolumn{2}{c}{Museum} & \multicolumn{4}{c}{Museum-year} \\ 
\cmidrule(r){3-4}\cmidrule(r){5-8} \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{Count} & \multicolumn{1}{l}{Mean} & \multicolumn{1}{l}{Mean} & \multicolumn{1}{l}{SD} & \multicolumn{1}{l}{Min.} & \multicolumn{1}{l}{Max.}\\ 
 \hline
  \multicolumn{8}{l}{\textbf{Founder}} \\ 
 & Gender - Male & $294$ & $0.584$ & $0.604$ & $0.49$ & $0$ & $1$ \\ 
   & Gender - Female & $79$ & $0.157$ & $0.166$ & $0.37$ & $0$ & $1$ \\ 
   & Gender - Couple & $130$ & $0.258$ & $0.231$ & $0.42$ & $0$ & $1$ \\ 
   & Founder died & $NA$ & $NA$ & $0.097$ & $0.30$ & $0$ & $1$ \\ 
   \multicolumn{8}{l}{\textbf{Museum}} \\ 
 & Self-Identification - Museum & $190$ & $0.378$ & $0.408$ & $0.49$ & $0$ & $1$ \\ 
   & Self-Identification - Foundation & $104$ & $0.207$ & $0.189$ & $0.39$ & $0$ & $1$ \\ 
   & Self-Identification - Collection & $69$ & $0.137$ & $0.130$ & $0.34$ & $0$ & $1$ \\ 
   & Self-Identification - Other & $140$ & $0.278$ & $0.274$ & $0.45$ & $0$ & $1$ \\ 
   & Founder name in Museum name & $240$ & $0.477$ & $0.477$ & $0.50$ & $0$ & $1$ \\ 
   & AN Ranking - Not Included & $NA$ & $NA$ & $0.802$ & $0.40$ & $0$ & $1$ \\ 
   & AN Ranking - Included & $NA$ & $NA$ & $0.144$ & $0.35$ & $0$ & $1$ \\ 
   & AN Ranking - Dropped & $NA$ & $NA$ & $0.053$ & $0.23$ & $0$ & $1$ \\ 
   \multicolumn{8}{l}{\textbf{Environment}} \\ 
 & PM density (country) & $NA$ & $NA$ & $0.450$ & $1.26$ & $0.00077$ & $27.26$ \\ 
   & Pop. (millions) within 10km & $NA$ & $NA$ & $1.337$ & $1.68$ & $0.000087$ & $10.81$ \\ 
   & Nbr PM within 10km & $NA$ & $NA$ & $1.778$ & $3.14$ & $0$ & $16$ \\ 
   & Great Recession (2008/09) & $NA$ & $NA$ & $0.076$ & $0.27$ & $0$ & $1$ \\ 
   & Covid Pandemic (2020/21) & $NA$ & $NA$ & $0.145$ & $0.35$ & $0$ & $1$ \\ 
   & Region - Africa & $8$ & $0.016$ & $0.012$ & $0.11$ & $0$ & $1$ \\ 
   & Region - Asia & $142$ & $0.282$ & $0.292$ & $0.45$ & $0$ & $1$ \\ 
   & Region - Europe & $248$ & $0.493$ & $0.497$ & $0.50$ & $0$ & $1$ \\ 
   & Region - Latin America & $23$ & $0.046$ & $0.042$ & $0.20$ & $0$ & $1$ \\ 
   & Region - North America & $72$ & $0.143$ & $0.138$ & $0.34$ & $0$ & $1$ \\ 
   & Region - Oceania & $10$ & $0.020$ & $0.019$ & $0.13$ & $0$ & $1$ \\ 
   \hline
\end{tabular}
\caption{Summary Statistics} 
\label{tbl:t_sumstats}
\end{table}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=16cm]{../figures/p_hazard.png}
\caption{\label{fig:p_hazard}Private Museum hazard function}
\end{figure}

\begin{figure}[htbp]
\centering
\includegraphics[width=14cm]{../figures/p_surv.png}
\caption{\label{fig:p_surv}Private Museum Survival probability}
\end{figure}

@@

Calculating such survival statistics allows (to a degree) to assess whether private museums differ in their longevity from comparable institutions.
So far only a few studies have investigated museum closing rates, and these have focused on the United States, likely primarily due to data availability reasons: 
Larger non-profits in the US have to file the IRS form 990 (or its variants) to maintain their tax-deductible status, and form 990 data is publicly available \parencite{Lecy_2023_core}.
This data has been used in many studies of non-profit populations and constitutes an effective comparison group for private museums as both share the same organizational form (non-profit) and unprofitable cultural sector environment.
So far three studies have used this data to investigate museum closure by calculating hazard rates not as a function of age but of calendar year:
\begin{itemize}
\item \textcite{Bowen_etal_1994_charitable} investigate the closing of 501(c)(3) museums in the 1981-1991 time period and, based on 271 (9.8\%) closures of a population of 2755, calculate average annual exit rates as 1.1\% (p.103).
\item \textcite{Gordon_etal_2013_insolvency} observe 35 closures based on 5,167 museum-years between 2000 and 2003 (p.368), resulting in an average annual closing rate of 0.68\% (p.377)\footnote{The difference to \textcite{Bowen_etal_1994_charitable} is likely due to exclusion of organizations with revenues below 150,000 USD.}.
\item \textcite{Hager_2001_vulnerability} has conducted the only study specifically on art museums (NTEE code A51); he observes 42 closures over a period of four years (1994-1997) from a starting population of 448 (p.383), corresponding to an average yearly closing rate of 2.4\%, or around 1.9\% under the more realistic assumption of effectively using a five-year time period.
\end{itemize}

@@

% latex table generated in R 4.3.3 by xtable 1.8-4 package
% Fri Sep 27 17:51:41 2024
\begin{table}[ht]
\centering
\begin{tabular}{p{0mm}ll}
  \hline 
 \multicolumn{1}{l}{} & \multicolumn{1}{l}{Variable} & \multicolumn{1}{l}{r\_pop4}\\ 
 \hline
  \multicolumn{3}{l}{\textbf{Founder}} \\ 
 & Gender - Female & $-.04 \; (0.34)$ \\ 
   & Gender - Couple & $-.14 \; (0.32)$ \\ 
   & Founder died & $.28 \; (0.43)$ \\ 
   \multicolumn{3}{l}{\textbf{Museum}} \\ 
 & Self-Identification - Foundation & $.20 \; (0.41)$ \\ 
   & Self-Identification - Collection & $-.45 \; (0.54)$ \\ 
   & Self-Identification - Other & $1.09 \; (0.30)^{***}$ \\ 
   & AN Ranking - Included & $.19 \; (0.34)$ \\ 
   & AN Ranking - Dropped & $.46 \; (0.50)$ \\ 
   & Founder name in Museum name & $.05 \; (0.28)$ \\ 
   \multicolumn{3}{l}{\textbf{Environment}} \\ 
 & PM density (country) & $.65 \; (0.34)$ \\ 
   & PM density$^{2}$ (country) & $-.03 \; (0.02)$ \\ 
   & Pop. (millions) within 10km & $.27 \; (0.09)^{**}$ \\ 
   & Nbr PM within 10km & $.26 \; (0.08)^{***}$ \\ 
   & Nbr PM (10km) * Pop (10km) & $-.09 \; (0.03)^{**}$ \\ 
   & Great Recession (2008/09) & $-1.59 \; (1.01)$ \\ 
   & Covid Pandemic (2020/21) & $.42 \; (0.29)$ \\ 
   \hline
 & Museums & $503$ \\ 
   & Museum-years & $6096$ \\ 
   & Closures & $68$ \\ 
   & log. Likelihood & $-339.68$ \\ 
   & AIC & $711.35$ \\ 
   & BIC & $746.87$ \\ 
   \hline 
 \multicolumn{3}{l}{\footnotesize{standard errors in parantheses.\textsuperscript{***}p $<$ 0.001;\textsuperscript{**}p $<$ 0.01;\textsuperscript{*}p $<$ 0.05.}} \\ 
\end{tabular}
\caption{Cox Proportional Hazards Regression Results} 
\label{tbl:t_reg_coxph}
\end{table}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=18cm]{../figures/p_surv_death.png}
\caption{\label{fig:p_surv_death}Comparison of Survival Estimates by Founder Death (95\% CI)}
\end{figure}

@@

\begin{figure}[htbp]
\centering
\includegraphics[width=18cm]{../figures/p_condmef.png}
\caption{\label{fig:p_condmef}Conditional effects of Regional PM Density and Population}
\end{figure}

Country-level measures of the private museum population show a marginally significant association with mortality (b=0.648, p=0.058).
\begin{figure}[htbp]
\centering
\includegraphics[width=18cm]{../figures/p_pred_heatmap.png}
\caption{\label{fig:p_pred_heatmap}Predicted Avg. Hazard Rate on Regional PM Density and Population (at available values)}
\end{figure}

@@

Similarly, characterizations of private museums as generally fragile \parencite{Adam_2020_close,Bechtler_Imhof_2018_future} are not supported here either.
While the descriptive comparison to other studies allows only preliminary conclusions, it still shows the importance of considering closings not in isolation, but in comparison to both non-closures and closures of comparable institutions.
In particular, the context of the growing private museum population deserves consideration, as large populations can generate dozens of closures without requiring high closing rates, especially when closures are considered over a span of several years or decades.
